Deeply Virtual Compton Scattering measurement off bound protons

### 2018-08-13 eg6-letters/incoherent/incoherent_prl.tex
implement Stepan's comments

One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
to see if significant nuclear effects are also visible within the GPD 
framework.  To explore this idea, we construct the ratio of $A_{LU}$ for bound 
protons to that on a free proton target. 
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
interpolation of the free proton asymmetries from  CLAS \cite{Girod:2007aa} as 
a function of the kinematical variable $x_B$. The $A_{LU}$ ratios show 
20\%-40\% lower asymmetries for a bound proton compared to the free proton 
mirroring a form of EMC effect but with a surprising large modification, in 
particular at low $x_B$. The measurements disagree with the off-shell 
\cite{simonetta_2} and the on-shell calculations that use the medium modified 
GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}. In 
particular, the difference becomes large at lower $x_B$, where the off-shell 
model predicts an enhancement of the ratio, where our experiment shows a sharp 
drop. This measurement shows that an important nuclear effect is missing from 
the existing models in order to explain this strong quenching of the BSA.

>>>>

One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
to see if significant nuclear effects are also visible within the GPD 
framework.  To explore this idea, we construct the ratio of $A_{LU}$ for bound 
protons to that on a free proton target. 
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
interpolation of the free proton asymmetries from  CLAS \cite{Girod:2007aa} as 
a function of the kinematical variable $x_B$. The $A_{LU}$ ratios show 
20\%-40\% lower asymmetries for a bound proton compared to the free proton 
mirroring a form of EMC effect but with a surprising large modification, in 
particular at low $x_B$. The measurements disagree with the off-shell 
\cite{simonetta_2} and the on-shell calculations that use the medium modified 
GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}. In 
particular, the difference becomes large at lower $x_B$, where the off-shell 
model predicts an enhancement of the ratio, while our experiment shows no sign 
of an increase of ratios. This measurement shows that an important nuclear 
effect is missing from the existing models in order to explain this strong 
quenching of the BSA.
